### 2022-08-08 head/abstracts.tex
Add files via upload

The second chapter, titled `Causal Networks with Neural Networks` is a co-authored work with Damir Filipović (SFI \& EPFL), Negar Kiyavash (EPFL) and Jalal Etesami (EPFL). We develop a data-driven framework to identify the interconnections between firms using an information-theoretic measure. 
This measure generalizes Granger causality and is capable of detecting nonlinear relationships within a network. 
Moreover, we develop an algorithm using recurrent neural networks and Granger causality to identify the interconnections of high-dimensional nonlinear systems. 
The outcome of this algorithm is the causal graph encoding the interconnections among the firms.
These causal graphs can be used as preliminary feature selection for another predictive model or for systemic risk management.
We evaluate the performance of our algorithm using both synthetic linear and nonlinear experiments and apply it to the daily stock returns of U.S. listed firms and infer their interconnections from 1990 to 2020. \\

@@

Cette thèse consiste en trois applications de techniques d'apprentissage automatique à la gestion des risques. \\

>>>>

The second chapter, titled `Causal Networks with Neural Networks` is a co-authored work with Damir Filipović (SFI \& EPFL), Negar Kiyavash (EPFL) and Jalal Etesami (EPFL). We develop a data-driven framework to identify the interconnections between firms using an information-theoretic measure. 
This measure generalizes Granger causality and is capable of detecting nonlinear relationships within a network. 
Moreover, we develop an algorithm using recurrent neural networks and Granger causality to identify the interconnections of high-dimensional nonlinear systems. 
The outcome of this algorithm is the causal graph encoding the interconnections among the firms.
These causal graphs can be used as preliminary feature selection for another predictive model or for systemic risk management.
We evaluate the performance of our algorithm using both synthetic linear and nonlinear experiments and apply it to the daily stock returns of US listed firms and infer their interconnections from 1990 to 2020. \\

@@

Cette thèse est composée de trois applications de techniques d'apprentissage automatique à la gestion des risques. \\

### 2022-08-08 head/acknowledgements.tex
Add files via upload

I wish to express my deepest gratitude to my supervisor, Damir Filipović, for his availability and continuous support during these five years. This thesis greatly benefited from his countless valuable comments and flow of smart ideas. He guided me and I learned a lot from him about doing research. For this, I am truly grateful.

Special thanks go to professor Michael Rockinger who convinced me to pursue a doctorate degree. He took me under his wing since my Bachelor studies and helped me becoming the researcher I am today. This thesis would not exist without him.

I would like to acknowledge the rest of my thesis committee, the professors Pierre Collin-Dufresne, Andreas Fuster and Simon Scheidegger for their advice and comments.

I am also thankful to the professors Elena Perazzi and Damien Challet. I was their TA for several years and they helped me become a better teacher.

During these years I had the chance to work with extremely nice and intelligent people. I am thankful to my colleagues and friends Antoine Didisheim and Coralie Jaunin for the many chess games and `bridge tours` around the campus.

>>>>

I wish to express my deepest gratitude to my supervisor, Professor Damir Filipović, for his availability and continuous support during these five years. This thesis greatly benefited from his countless valuable comments and flow of smart ideas. He guided me and I learned a lot from him about doing research. For this, I am truly grateful.

Special thanks go to Professor Michael Rockinger who convinced me to pursue a doctorate degree. He took me under his wing since my Bachelor studies and helped me becoming the researcher I am today. This thesis would not exist without him.

I would like to acknowledge the rest of my thesis committee, Professors Pierre Collin-Dufresne, Andreas Fuster and Simon Scheidegger for their advice and comments.

I am also thankful to Professors Elena Perazzi and Damien Challet. I was their TA for several years and they helped me become a better teacher.

During these years I had the chance to work with extremely nice and intelligent people. I am thankful to my colleagues and friends Antoine Didisheim and Coralie Jaunin for the many chess games and `bridge tours` around the campus. I am also very grateful to my longstanding friend Christophe George for the proofreading of this thesis.
